\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-12 doc/USER_MANUAL/manual_SPECFEM3D.tex
second partial update of list of authors

The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University, then Caltech and Princeton, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at IPG in Paris, France from 1994 to 1997. Since then it has been developed and maintained by a development team: in alphabetical order, Emiljana Jorgji, Dimitri Komatitsch, Nicolas Le Goff, Pieyre Le Loher, Roland Martin, David Mich\'ea, Jeroen Tromp \toall{add full list of developers here and update the AUTHORS file accordingly}.

>>>>

The SPECFEM3D package was first developed by Dimitri Komatitsch and Jeroen Tromp at Harvard University, then Caltech and Princeton, USA, starting in 1998, based in part on earlier work by Dimitri Komatitsch and Jean-Pierre Vilotte at IPG in Paris, France from 1994 to 1997. Since then it has been developed and maintained by a development team: in alphabetical order,
Emanuele Casarotti,
Min Chen,
Vala Hj\"orleifsd\'ottir,
Emiljana Jorgji,
Sue Kientz,
Dimitri Komatitsch,
Qinya Liu,
Yang Luo,
Nicolas Le Goff,
Pieyre Le Loher,
Alessia Maggi,
Roland Martin,
Dennis McRitchie,
David Mich\'ea,
Daniel Peter,
Brian Savage,
Leif Strand,
Carl Tape,
Jeroen Tromp
\toall{add full list of developers here and update the AUTHORS file accordingly}.
